---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Analysis of Matched Interactions across Tissues

The mixtR package (Matched Interactions across Tissues) contains the computational 
and statistical methods for identifying and exploring associations between sets
of genes or molecular processes across tissues. Learn more in the vignette `Introduction to mixtR`.   

The web application framework is open sourced at http://github.com/fjukstad/mixt and 
use the mixtApp R wrapper package available at https://github.com/vdumeaux/mixtApp.
Learn more in the vignette `MIxT web application`. 

## Installation

```{r, eval = FALSE}
# Install packages from GitHub
devtools::install_github("vdumeaux/mixtR")
devtools::install_github("vdumeaux/mixtApp")
```

## References

* Dumeaux V, Fjukstad B, Lund E, Bongo LA, Hallett M. MIxT: Matched Interaction Across Tissue analysis and visualization (manuscript).
* Dumeaux V, Fjukstad B, Fjosne HE, Frantzen J-O, Holmen MM, Rodegerdts E, Schlichting E, Børresen-Dale AL, Bongo LA, Lund E, Hallett M (2017) 
[Interactions between the tumor and the blood systemic response of breast cancer patients](http://journals.plos.org/ploscompbiol/article?id=10.1371/journal.pcbi.1005680). PLoS Comput Biol 13(9): e1005680.
* Fjukstad B, Dumeaux V, Olsen KS, Lund E, Hallett M, and Bongo LA (2017). [Building Applications for Interactive Data Exploration in Systems Biology](https://dl.acm.org/citation.cfm?id=3107481). 
In Proceedings of the 8th ACM International Conference on Bioinformatics, Computational Biology, and Health Informatics (Boston, Massachusetts, USA: ACM), pp. 556-561.

## Live website
* [Tumor and blood transcriptional profiles from breast cancer patients ](http://mixt-blood-tumor.bci.mcgill.ca/)
* [Tumor and stroma transcriptional profiles from breast cancer patients ](http://mixt-tumor-stroma.bci.mcgill.ca/)
